\parbox{\linewidth}{\centering Bayesian Non-Parametric Inference in Multivariate\\ Peaks-over-Thresholds Models}

### 2022-12-18 poster2.tex
blah

    \begin{tikzfigure}[Energy Score for recovering distribution of simulated data for a variety of dimensions, number of mixture components in generating distribution (lower is better).]
        \centering 
        \includegraphics[width=0.25\textwidth,height=0.09\textwidth]{images/simulation_score}
    \end{tikzfigure}

@@

    \begin{tikzfigure}[Pairwise extremal dependence coefficients for IVT data using PRG-G model.]
    \centering
    \includegraphics[width=0.95\linewidth]{./images/chi_ij_c}
    \end{tikzfigure}
    Effectively, using the model in this way, we are capturing the spatial dependence structure for extremes in the IVT.
    }
\end{subcolumns}

>>>>

    \begin{tikzfigure}[Energy Score vs number of dimensions for recovering distribution of simulated data,\\for varying number of mixture components in generating distribution (lower is better).]
        \centering 
        \includegraphics[width=0.25\textwidth,height=0.08\textwidth]{images/simulation_score_es}
    \end{tikzfigure}

@@

    \begin{tikzfigure}[Pairwise extremal dependence coefficients\\ for IVT data using PRG-G model.]
    \centering
    \includegraphics[width=0.95\linewidth]{./images/chi_ij_c}
    \end{tikzfigure}
    Effectively, using the model in this way, we are capturing the spatial dependence structure for extremes in the IVT.
    }
\end{subcolumns}
